---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# contactparser

<!-- badges: start -->
<!-- badges: end -->

The contactparser package was designed to parse and reformat the [Contacts table](https://www.nhlbiwgs.org/contact-filter) on the TOPMed website.


## Installation

You can install the released version of contactparser from [github](https://github.com/UW-GAC/contactparser) with:

``` r
# install.packages("devtools") 
devtools::install_github("UW-GAC/contactparser")
```

## Example

This package has one primary function to read, parse, and reformat the contacts table.
It starts with either a csv file or an html file, parses it, and reshapes the table so that it can easily be filtered by TOPMed study, project, or contact type (PI, Co-PI, Contact, etc.).

First, export the table to a csv file with the "export" button.
Then call:
```{r csv-example}
library(contactparser)
csv_file <- system.file(package = "contactparser", "testdata", "example.csv")
parse_contact_table(csv_file)
```

You can also save the webpage as an html file and parse the contact table from the html:
```{r html-example}
library(contactparser)
html_file <- system.file(package = "contactparser", "testdata", "example.html")
parse_contact_table(html_file)
```

